---
title: "simpleRegress"
author: "Aeilani Felix"
date: "Spring 2024"
output: html_document
---

## Compare all models
Predict LENGTH based on the variables other than LENGTH. Then order them from worst to best by its value of Adjusted-Rsquared (bigger is better), or by RSE (residual standard error) where smaller is better. 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## make a simple regression model

```{r}
bears <- read.csv(file="BEARS.csv",header = TRUE)
#adjust factors to be factors
bears$SEX<- as.factor(bears$SEX)
bears$MONTH<- as.factor(bears$MONTH)
```

## Model LENGTH ~ NECK  this is an example  

```{r}
simpNECK <- lm(LENGTH~NECK,data=bears)
plot(LENGTH~NECK,data=bears)
abline(simpNECK)
summary.lm(simpNECK)
```

The results from this graph show us that the variable of NECK has a strong effect of finding the length of a bear by an adjusted r-squared value of 0.75.

```{r}
simpAGE <- lm(LENGTH~AGE,data=bears)
plot(LENGTH~AGE, data=bears)
abline (simpAGE)
summary.lm(simpAGE)
```

This second graph gives us a value of an adjusted r-squared 0.50. 

## Head Length

```{r}
simp <- lm(LENGTH~HEADLEN,data=bears)
plot(LENGTH~HEADLEN,data=bears)
abline(simp)
summary.lm(simp)
```

The adjusted R-squared for LENGTH ~ HEADLEN is 0.84.

## Head Width

```{r}
simp <- lm(LENGTH~HEADWTH,data=bears)
plot(LENGTH~HEADWTH,data=bears)
abline(simp)
summary.lm(simp)
```

The adjusted R-squared for LENGTH ~ HEAD WIDTH is 0.53.

## Chest

```{r}
simp <- lm(LENGTH~CHEST,data=bears)
plot(LENGTH~CHEST,data=bears)
abline(simp)
summary.lm(simp)
```

The adjusted R-Squared for LENGTH ~ CHEST is 0.79.

## Weight

```{r}
simp <- lm(LENGTH~WEIGHT,data=bears)
plot(LENGTH~WEIGHT,data=bears)
abline(simp)
summary.lm(simp)
```

The adjusted R-squared for LENGTH ~ WEIGHT is 0.74.



Based off these two simple models of the bears length, between NECK and AGE


